%-------------------------
% Cover letter — software engineering variant
% Tailor per application by editing the THREE commands below, nothing else.
% Build: pdflatex cover-letter-swe.tex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}
\pdfgentounicode=1

\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{0.6in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{0.8in}
\raggedbottom
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% ===== TAILOR THESE THREE LINES PER APPLICATION =====
\newcommand{\company}{[COMPANY]}
\newcommand{\role}{[ROLE TITLE]}
\newcommand{\hook}{[ONE SENTENCE: the specific product, system, or problem at \company{} you want to work on, and why your background fits it. Delete this bracket text.]}
% =====================================================

\begin{document}

\begin{center}
    {\Huge \scshape Suleyman Kiani} \\ \vspace{3pt}
    \small Burlington, ON $\cdot$ +1 (289) 788-8260 $\cdot$ \href{mailto:suley.kiani@outlook.com}{\underline{suley.kiani@outlook.com}} $\cdot$ \href{https://suleyman.io}{\underline{suleyman.io}} $\cdot$ \href{https://github.com/kianis4}{\underline{github.com/kianis4}}
\end{center}

\vspace{8pt}
\today

Dear \company{} Hiring Team,

I am applying for the \role{} position. \hook{}

I build production systems end to end and run them afterward. Through my studio, SKomp Studio, I designed, shipped, and now operate a multi-tenant booking-and-payments platform for a paying client: \$40K+ CAD processed, 500+ registered users, and a codebase held to 1,600+ automated tests with idempotent payment processing and webhook signature verification, because money-handling code has to be boring and correct. Separately, I built and operate a self-hosted multi-agent platform that runs 30+ scheduled automations: email-triggered workers that turn real document packages into ready-to-file output in minutes, each one sandboxed in a kernel-namespace jail behind fail-closed gates, with an autonomous overnight pipeline that builds and tests projects behind a 12-check publish gate. It is the most honest education available in what agentic systems actually require: permission boundaries, cost ceilings, and verification loops, not demos.

My day job sharpens the same instincts from the business side. As an Associate Account Manager at Mitsubishi HC Capital Canada, I carry an equipment-finance sales book, and I have shipped internal software the desk uses daily: a quoting engine that replaced 13 abandoned Excel calculators and matches TValue, the industry lease-math standard, to the penny under 72 automated tests, and an AI document-validation service that went through the company's first internal innovation review and now audits deal packages unattended. I am finishing an MEng in Computing \& Software at McMaster, where my research applies formal methods to LLM citation faithfulness.

Everything above is inspectable: the platform is live, the site at suleyman.io documents the architecture, and I am happy to walk through any of it in depth. I would welcome the chance to bring this mix of shipped systems and production judgment to \company{}.

Sincerely,

Suleyman Kiani

\end{document}
