%-------------------------
% Cover letter — INTERNAL MHCCNA applications (promotion case)
% Tailor the THREE commands below. Notes:
%  - Internal title is Sales Analyst; this letter assumes the reader knows you.
%  - Names internal programs deliberately (STP track) — INTERNAL USE ONLY,
%    never send this variant outside MHCCNA.
%  - Deliberately does NOT mention SKomp Studio or any outside work.
% Build: pdflatex cover-letter-mhc-internal.tex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}
\pdfgentounicode=1

\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{0.6in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{0.8in}
\raggedbottom
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% ===== TAILOR THESE THREE LINES PER APPLICATION =====
\newcommand{\role}{[POSTED ROLE TITLE]}
\newcommand{\hiringmgr}{[HIRING MANAGER NAME or "Hiring Team"]}
\newcommand{\hook}{[ONE SENTENCE: what this specific role/desk needs next and why you are positioned to deliver it. Delete this bracket text.]}
% =====================================================

\begin{document}

\begin{center}
    {\Huge \scshape Suleyman Kiani} \\ \vspace{3pt}
    \small Sales Analyst, Equipment Finance $\cdot$ Burlington, ON $\cdot$ \href{mailto:skiani@mhccna.com}{\underline{skiani@mhccna.com}}
\end{center}

\vspace{8pt}
\today

Dear \hiringmgr,

I am applying for the \role{} posting. You already know my day-to-day work, so this letter is a statement of intent rather than an introduction. \hook{}

The record since I joined in September: over quota every month since my second month in the seat, including over \$4M funded against the \$2M monthly new-business target in each of April and May. I support 10+ vendor relationships across Ontario, Alberta, BC, and Quebec, and I work files end to end: spreads, debt ratios and FCCR, four-block submissions to credit, documentation, and funding. Beyond the book, I carried the collections scorecard through STP Gate 1 and now lead its Phase 1 rollout with the credit and portfolio teams, and I built the quoting engine the desk uses in place of the legacy calculators, validated to the penny against TValue.

What the next role asks for that I am already doing: owning vendor conversations rather than supporting them, presenting submissions to credit directly, and carrying independent coverage of a territory. The pieces I would be stepping into, I have been practicing inside my current scope; the pieces I already own, the numbers above speak for.

I would welcome the conversation. % OPTIONAL line, uncomment to use:
% My current leadership can speak to all of the above directly; I am glad to arrange it.

Sincerely,

Suleyman Kiani

\end{document}
