%-------------------------
% Cover letter — equipment finance / account manager variant
% Tailor per application by editing the THREE commands below, nothing else.
% For INTERNAL MHCCNA postings: see the alternate hook guidance in the comment.
% Build: pdflatex cover-letter-finance.tex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}
\pdfgentounicode=1

\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{0.6in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{0.8in}
\raggedbottom
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% ===== TAILOR THESE THREE LINES PER APPLICATION =====
% For internal MHCCNA roles, \hook can reference the team/program directly,
% e.g. "Having built the desk's quoting and document tooling, I want to bring
% that same operating discipline to <team>."
\newcommand{\company}{[COMPANY]}
\newcommand{\role}{[ROLE TITLE]}
\newcommand{\hook}{[ONE SENTENCE: why this company's vendor programs, asset classes, or market position make this the book you want to build. Delete this bracket text.]}
% =====================================================

\begin{document}

\begin{center}
    {\Huge \scshape Suleyman Kiani} \\ \vspace{3pt}
    \small Burlington, ON $\cdot$ +1 (289) 788-8260 $\cdot$ \href{mailto:suley.kiani@outlook.com}{\underline{suley.kiani@outlook.com}} $\cdot$ \href{https://www.linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}}
\end{center}

\vspace{8pt}
\today

Dear \company{} Hiring Team,

I am applying for the \role{} position. \hook{} By way of introduction: in my current seat I have funded \$4M against a \$2M monthly target in each of April and May 2026.

I am an Associate Account Manager at Mitsubishi HC Capital Canada, carrying a vendor-sales equipment-finance book across construction, transportation, and material-handling assets. I have exceeded my monthly new-business quota every month since my second month in the seat, and I work deals end to end: quote, structure (FMV, capital, and vendor-finance), credit submission, documentation, and funding. I manage 10+ vendor relationships across Ontario, Alberta, BC, and Quebec, and the desk runs on TValue, InfoLease, Salesforce, Excel, and Power BI; I am fluent in all of them.

What I add beyond the book is that I build the tooling most desks wish they had. I reverse-engineered our manufacturers' lease and subsidy math into a quoting engine that replaced 13 abandoned Excel calculators across all 11 product lines and matches TValue to the penny. I co-designed a predictive collections scorecard with our credit and portfolio teams across \$17--18M of in-recovery assets and carried the business case through approval. And I cut pre-funding document review from one to two hours to about five minutes with an AI validation service, now piloting on 50+ live deal packages, that went through the company's first internal innovation review. Faster, cleaner funding packages mean vendors get paid sooner, and vendors who get paid sooner send the next deal.

I also run a small software studio whose client platform has processed \$40K+ CAD, which taught me what it means to own a client relationship where renewals depend entirely on delivery. That is the same muscle an account manager uses every day.

I would welcome the chance to talk about how this mix of quota performance, full-cycle deal work, and desk-level tooling would serve \company{}.

Sincerely,

Suleyman Kiani

\end{document}
