%-------------------------
% Resume in Latex
% Author : Suleyman Kiani
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----------Header-----------
\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{2pt}
    \small \scshape Software Engineer $\cdot$ Equipment Finance $\cdot$ Fintech / Finance Platforms \\ \vspace{2pt}
    \small +1 (289) 788-8260 $|$ \href{mailto:kianis4@mcmaster.ca}{\underline{kianis4@mcmaster.ca}} $|$ \href{https://www.linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}} $|$ \href{https://github.com/kianis4}{\underline{github.com/kianis4}} $|$ \href{https://suleyman.io}{\underline{suleyman.io}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\vspace{2pt}
\small{Software engineer who ships production systems: a multi-tenant SaaS billing live customers on \textbf{Square}, an event-driven \textbf{.NET} microservices pipeline, and an ML autodiff engine built from scratch. I bring an underwriter's instinct for correctness from the equipment-finance desk, where I fund \textbf{200\% of monthly quota} at Mitsubishi HC Capital while completing an MEng in Computing \& Software. Targeting fintech and finance-platform engineering.}
\vspace{-6pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Master of Engineering (MEng), Computing and Software}{Sept. 2025 - Dec. 2026 (expected)}
      \resumeItemListStart
        \resumeItem{Year 1 complete with \textbf{A+} in Simple Type Theory and Microservices-Oriented Architectures.}
      \resumeItemListEnd
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Applied Science (BASc), Computer Science}{Sept. 2018 - Nov. 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Associate Account Manager, Equipment Finance}{Sept. 2025 - Present}
      {Mitsubishi HC Capital Canada}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Built a \textbf{TypeScript} web quoting app consolidating \textbf{13 manufacturer-specific pricing models} into one validated tool used on live deals, eliminating a class of manual rate-calculation errors.}
        \resumeItem{Contributed \textbf{Python} modeling to a cross-functional predictive default-risk model and built \textbf{Power BI} portfolio and variance analyses supporting credit decisions.}
        \resumeItem{Underwrite and structure equipment leases and loans (FMV, capital, vendor-finance) across construction, transportation, and material-handling; spread financial statements and compute coverage and net-investment metrics.}
        \resumeItem{Funded \textbf{\$4M against a \$2M monthly target (200\% of quota)} in April and May 2026, exceeding funding quota every month since my second month in the role.}
      \resumeItemListEnd
    \resumeSubheading
      {Junior Web Developer}{May 2021 - Aug. 2022}
      {Giftcash Inc.}{Remote}
      \resumeItemListStart
        \resumeItem{Migrated a legacy \textbf{Python}/\textbf{Django} monolith to a \textbf{Node.js} \textbf{AWS Lambda} serverless architecture and tuned \textbf{PostgreSQL} indexing and caching; p95 on the balance-verification endpoint dropped from $\sim$340ms to $\sim$210ms.}
        \resumeItem{Automated balance-verification workflows with \textbf{Puppeteer} and built \textbf{GitHub Actions} CI/CD pipelines, replacing a manual multi-step release with a one-click deploy.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://www.solsticepilates.ca/}{\textbf{Skomp Studio}} (multi-tenant studio SaaS) $|$ \emph{Next.js, React, Prisma/Neon, Square, AWS}}{2025 - Present}
          \resumeItemListStart
            \resumeItem{Built a multi-tenant TypeScript SaaS processing live \textbf{Square} payments for a paying studio; row-level tenant isolation and a \textbf{5{,}000+ test} Vitest suite gate every release, with zero cross-tenant leaks or billing incidents since launch.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/kianis4/Deal-Flow-Sandbox}{\textbf{DealFlow Sandbox}} (event-driven microservices) $|$ \emph{.NET, RabbitMQ, PostgreSQL, Docker}}{2025}
          \resumeItemListStart
            \resumeItem{Modeled an equipment-finance pipeline as decoupled \textbf{.NET} microservices over \textbf{RabbitMQ}/MassTransit, replacing a 15--20 minute manual party-exposure lookup with a sub-second API call.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://www.applify-ai.com/}{\textbf{Applify AI}} (AI r\'esum\'e-tailoring SaaS) $|$ \emph{Next.js, PostgreSQL, Stripe, LLM APIs}}{2025 - Present}
          \resumeItemListStart
            \resumeItem{Shipped an AI r\'esum\'e-tailoring product to \textbf{$\sim$150 paying users} with \textbf{Stripe} subscriptions and authenticated, per-user data isolation.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/kianis4}{\textbf{Micrograd Engine}} (from-scratch autodiff) $|$ \emph{Python, Jupyter}}{2025}
          \resumeItemListStart
            \resumeItem{Implemented a from-scratch automatic-differentiation engine (\texttt{Value}, \texttt{Neuron}, \texttt{Layer}, \texttt{MLP}) with backpropagation to ground ML fundamentals.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Python, SQL, C/C++, Java, Swift, JavaScript, Bash} \\
     \textbf{Frameworks}{: Next.js, React, Node.js, FastAPI, .NET / ASP.NET Core, Prisma, React Native, PyTorch} \\
     \textbf{Data \& Cloud}{: PostgreSQL (Neon), MongoDB, AWS, Vercel, GCP, Docker, RabbitMQ, GitHub Actions} \\
     \textbf{AI \& Finance}{: Claude API / agentic workflows, RAG \& vector search, MCP; credit analysis, financial-statement spreading, lease/loan structuring, Power BI}
    }}
\end{itemize}


\end{document}
