%-------------------------
% Resume in Latex (finance-first variant)
% Author : Suleyman Kiani
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%-----------HEADER-----------
\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{3pt}
    \small Equipment Finance $\cdot$ Credit \& Analytics $\cdot$ Engineer-Built Tooling \\ \vspace{3pt}
    \small +1 (289) 788-8260 $|$ \href{mailto:suley.kiani@outlook.com}{\underline{suley.kiani@outlook.com}} $|$ \href{https://www.linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}} $|$ \href{https://github.com/kianis4}{\underline{github.com/kianis4}} $|$ \href{https://suleyman.io}{\underline{suleyman.io}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\vspace{2pt}
\small{Equipment-finance professional who also builds the tooling the desk runs on. At Mitsubishi HC Capital I carry a vendor-sales book funding \textbf{200\% of monthly new-business target} and reverse-engineered manufacturer lease and subsidy math into a quoting engine that \textbf{replaced 13 Excel calculators} and matches the industry-standard \textbf{TValue} to the penny. I pair credit, amortization, and portfolio fluency with the ability to ship the software that operationalizes them.}
\vspace{-4pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Associate Account Manager, Equipment Finance}{Sept. 2025 -- Present}
      {Mitsubishi HC Capital Canada}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Carry a vendor-sales equipment-finance book across construction, transportation, and material-handling assets: funded \textbf{\$4M against a \$2M monthly new-business target (200\%)} and have \textbf{exceeded quota every month since my second month}.}
        \resumeItem{Underwrite and structure leases and loans across \textbf{FMV, capital, and vendor-finance structures}, working deals from quote through credit submission, documentation, and funding.}
        \resumeItem{Designed a \textbf{predictive collections scorecard} with the credit and portfolio teams: it auto-triages low-risk accounts and ranks the rest by recovery priority across about \textbf{\$17--18M in recovery}, where \textbf{each 1\% of recovery improvement is worth about \$1M}; owned the business case and won approval.}
        \resumeItem{Built an \textbf{AI document-validation prototype} for deal-funding review and carried it through the company's first internal innovation review; it now audits live deal packages unattended and turns power-of-attorney and pre-funding packages around \textbf{in minutes}.}
      \resumeItemListEnd
    \resumeSubheading
      {Founder}{Jan. 2024 -- Present}
      {SKompXcel Academic Solutions}{Remote}
      \resumeItemListStart
        \resumeItem{Founded a mentorship practice and have coached \textbf{100+ learners} through algorithms, systems design, and interview preparation, owning the client pipeline end to end.}
      \resumeItemListEnd
    \resumeSubheading
      {Junior Web Developer}{May 2021 -- Jun. 2022}
      {Giftcash Inc.}{Remote}
      \resumeItemListStart
        \resumeItem{Built payout and gift-card valuation services on a \textbf{Node.js / AWS Lambda} stack and automated balance verification, replacing manual per-card checks.}
        \resumeItem{Migrated the legacy Django monolith to serverless, tuned \textbf{PostgreSQL} on hot read paths, and stood up \textbf{CI/CD}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Finance \& Credit}{: Equipment \& lease structuring, credit analysis, amortization math (PMT/PV/FV/RATE/IRR, TValue-validated), subsidy \& blended-rate modeling, credit-scorecard \& recovery modeling} \\
     \textbf{Tools}{: TValue, Excel (advanced), InfoLease, Power BI, SQL} \\
     \textbf{Engineering}{: TypeScript, Python, Next.js / React, Node.js, PostgreSQL, multi-agent automation, payments integrations (Square, Stripe)}
    }}
\end{itemize}

%-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Personal Agentic OS} $\cdot$ multi-agent automation for real document workflows $|$ \emph{Python, TypeScript, Claude}}{2026}
          \resumeItemListStart
            \resumeItem{Built and run a \textbf{self-hosted multi-agent system} automating the document side of equipment finance: email-triggered services that validate funding packages and produce power-of-attorney and registration documents \textbf{in minutes}, ready to file.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://www.solsticepilates.ca/}{\textbf{Solstice Pilates}} $\cdot$ booking \& payments platform built solo $|$ \emph{Next.js, Prisma, Square}}{2025 -- Present}
          \resumeItemListStart
            \resumeItem{Designed and shipped a studio's \textbf{entire booking-and-payments platform} solo (Square payments, recurring memberships): \textbf{500+ registered users}, \textbf{\$20K+ CAD processed}, and \textbf{revenue-losing payment bugs} caught and fixed in production.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {MEng, Computing \& Software (in progress)}{Sept. 2025 -- Dec. 2026}
      \resumeItemListStart
        \resumeItem{Year 1 complete: \textbf{A+ in Simple Type Theory and Microservices-Oriented Architectures}.}
      \resumeItemListEnd
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {BASc (Honours), Computer Science}{Sept. 2018 -- Nov. 2024}
  \resumeSubHeadingListEnd

\end{document}
