%-------------------------
% Resume in Latex (2-page)
% Author : Suleyman Kiani
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%-----------HEADER-----------
\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{3pt}
    \small Software Engineer $\cdot$ Fintech \& Agentic Systems \\ \vspace{3pt}
    \footnotesize Burlington, ON $|$ +1 (289) 788-8260 $|$ \href{mailto:suley.kiani@outlook.com}{\underline{suley.kiani@outlook.com}} $|$ \href{https://www.linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}} $|$ \href{https://github.com/kianis4}{\underline{github.com/kianis4}} $|$ \href{https://suleyman.io}{\underline{suleyman.io}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\vspace{2pt}
\small{Software engineer who builds the tooling a finance desk actually runs on: a production quoting engine matching TValue, the industry lease-math standard, to the penny; a multi-tenant booking-and-payments platform processing real client revenue; a self-hosted agentic platform with sandboxed workers and fail-closed gates. Equipment-finance experience at Mitsubishi HC Capital gives me domain fluency most engineers don't have. Finishing an MEng in Computing \& Software at McMaster.}
\vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {MEng, Computing \& Software (Distributed Systems, Microservices \& Applied ML)}{Sept. 2025 -- 2026}
      \resumeItemListStart
        \resumeItem{Research with Dr. Farmer and Dr. Paige: TLA+ and SMT2 specifications for an LLM citation-faithfulness gating layer, verifying that a study companion's generated notes stay attributable to their sources.}
        \resumeItem{\textbf{A+} in Simple Type Theory and Microservices-Oriented Architectures.}
        \resumeItem{Built \href{https://www.suleyman.io/architecture}{\underline{\textbf{PodcastHub}}} for the distributed-systems course: five event-driven microservices (Node/Express, Python/FastAPI) in six containers with a dedicated FFmpeg worker, choreographed over a RabbitMQ topic exchange with MinIO presigned-URL storage and a RabbitMQ-to-WebSocket notification bridge.}
      \resumeItemListEnd
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {BASc (Honours), Computer Science}{Sept. 2018 -- Nov. 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Associate Account Manager (Internal Software Engineering)}{Sept. 2025 -- Present}
      {Mitsubishi HC Capital Canada}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Rebuilt \textbf{13 abandoned Excel calculators} (30--45 sheets each) as one Next.js / React app covering all 11 product lines; reverse-engineered the manufacturers' lease and subsidy math and pinned \textbf{penny-parity with TValue} with 72 automated tests; the desk's one trusted pricing tool.}
        \resumeItem{Untangled three structurally different subsidy formulas, proved three regional dealer workbooks were re-skins of one template, and collapsed them into shared calculation engines; authored the architecture and handoff documentation that lets the company's IT org own and extend the tool.}
        \resumeItem{Built an AI document-validation prototype (OCR + ML + rules) for deal-funding review and took it through the company's first internal innovation review; in pilot on \textbf{50+ live deal packages}, it cuts review from \textbf{1--2 hours to about 5 minutes}, each verdict logged to a per-deal audit trail.}
        \resumeItem{Designed a predictive collections scorecard with the credit and portfolio teams: a dual-track model that auto-triages low-risk accounts and scores the rest by recovery priority across about \textbf{\$17--18M} of assets in recovery; each one-point lift in the portfolio recovery rate is worth about \textbf{\$1M}. Owned the business case, won approval, and now lead the Phase 1 rollout with the desk's Power BI portfolio and variance reporting behind it.}
        \resumeItem{Carry the desk's sales book: funded \textbf{\$4M against a \$2M monthly target} (200\%) in each of April and May 2026; over quota every month since month two.}
      \resumeItemListEnd
    \resumeSubheading
      {Founder \& Software Engineer}{Jan. 2024 -- Present}
      {SKomp Studio}{Remote}
      \resumeItemListStart
        \resumeItem{Founded a software studio and designed, shipped, and now operate its flagship client platform, \href{https://www.solsticepilates.ca/}{\underline{\textbf{Solstice Pilates}}} (solsticepilates.ca), solo: a multi-tenant booking-and-payments system (\textbf{37-model Prisma schema}, \textbf{106 API routes}) with scheduling, FIFO waitlists and capacity gating, Square payments and recurring memberships with tax handling, digital waivers, and a 23-page admin portal.}
        \resumeItem{Runs live operations (\textbf{\$40K+ CAD processed} across \textbf{850+ bookings}, 450+ registered users) and ships a client-driven roadmap on \textbf{1,600+ automated tests}, including 70 Playwright e2e specs gating merges as required checks against every Vercel preview, shadow-DB checks across all 49 versioned migrations, and Gitleaks secret scanning in CI.}
        \resumeItem{Engineered for money-handling correctness: idempotent Square payment processing, webhook signature verification, and row-level tenant isolation via a scoped Prisma client.}
        \resumeItem{Landed five production fixes in parallel in one agent-orchestrated session, each in its own git worktree with its own test-and-verify loop, merged through branch-protected PRs.}
        \resumeItem{Coached \textbf{100+ learners} through algorithms, systems design, and technical-interview prep in the studio's mentorship arm, taking each engagement from acquisition through delivery.}
      \resumeItemListEnd
    \resumeSubheading
      {Junior Web Developer}{May 2021 -- Jun. 2022}
      {Giftcash Inc.}{Remote}
      \resumeItemListStart
        \resumeItem{Migrated a legacy Python / Django monolith to Node.js on AWS Lambda, trading always-on server overhead for per-request billing, and tuned PostgreSQL with indexing, caching, and query rewrites that killed the sequential scans behind the gift-card lookup flow.}
        \resumeItem{Automated gift-card balance verification with a Puppeteer + Axios pipeline and stood up Jenkins and GitHub Actions CI/CD so merges deployed without manual release steps.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\href{https://www.suleyman.io/architecture}{\underline{\textbf{Personal Agentic OS}}} $\cdot$ multi-agent automation platform $|$ \emph{Python, TypeScript, Claude, systemd, Tailscale}}{2026}
          \resumeItemListStart
            \resumeItem{Operate the self-hosted multi-agent platform behind the document-validation service above: \textbf{30+ scheduled automations} and email-triggered workers that validate funding-deal packages in minutes, containing prompt-injection risk from untrusted attachments.}
            \resumeItem{Every untrusted worker runs in a kernel-namespace sandbox (bubblewrap) behind fail-closed gates; secrets live in a 1Password vault, backups run nightly off-site, and a health watchdog emails on problem-state transitions.}
            \resumeItem{Runs an autonomous overnight pipeline that picks a candidate idea, builds and tests it in an isolated git worktree, and publishes behind a \textbf{12-check eval gate} (dependency vulnerabilities, secret hygiene, origin integrity, a model-based validator), refusal reasons persisted to an audit log; monitored from an iOS app over Tailscale; heavy jobs dispatch to a second compute node through a FastAPI work queue with artifact upload.}
            \resumeItem{Includes a fully local RAG stack (qwen2.5 on an RTX 3080) returning cited answers in \textbf{about 4s} at zero API cost, plus a Whisper voice-note router that files each note to the right project, tuned against Recall@10.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://mike-ross.ca/}{\underline{\textbf{Mike Ross AI}}} $\cdot$ legal RAG assistant (Delta Hacks 12) $|$ \emph{LangGraph, Gemini 2.0, MongoDB Atlas, FastAPI}}{2026}
          \resumeItemListStart
            \resumeItem{Built a legal assistant that answers Canadian-law questions with schema-enforced, quote-grounded citations: a LangGraph state machine routes intent and runs jurisdiction-aware vector retrieval (provincial queries auto-merge federal law) over a \textbf{16,000-chunk} corpus of seven Canadian statutes on MongoDB Atlas.}
            \resumeItem{Wired Gemini 2.0 Flash structured outputs to a FastAPI backend with multi-turn thread memory and a draft-to-PDF pipeline for legal notices; live at mike-ross.ca.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{LLM Study Companion} $\cdot$ MEng research system $|$ \emph{FastAPI, Next.js, pgvector}}{2026}
          \resumeItemListStart
            \resumeItem{Building the system around the research: event-driven hexagonal services (FastAPI, Next.js, Postgres + pgvector), AssemblyAI lecture transcription, and Cohere reranking, with the TLA+/SMT2-specified citation gate as the publish oracle for generated study notes.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://applify-ai.com/}{\underline{\textbf{Applify AI}}} $\cdot$ resume-tailoring SaaS $|$ \emph{Next.js, Inngest, OpenAI}}{2025 -- Present}
          \resumeItemListStart
            \resumeItem{Production SaaS that tailors a resume to a job posting: seven durable Inngest job types drive the OpenAI Responses API with schema-validated outputs, including a \textbf{self-correcting page-fit loop} (up to 20 checkpointed iterations of bullet reduction, LaTeX recompile, page-count check, about 65 durable steps per document); Stripe billing with idempotent webhooks; 98-test CI suite.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://suleyman.io/}{\underline{\textbf{suleyman.io}}} $\cdot$ personal site built as a product $|$ \emph{Next.js 16, Prisma, Neon, Vercel}}{2026}
          \resumeItemListStart
            \resumeItem{The site is a command-center HUD with a working in-browser terminal (custom REPL, commands and games), live Spotify visualizations, a GitHub-language constellation fed by the GitHub API, and a database-backed resume pipeline serving versioned resume variants from Postgres.}
            \resumeItem{The resume pipeline behind this document runs on it: server-seeded Prisma rows, versioned LaTeX variants, and ATS-audited PDF builds.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://overload-pro.com/}{\underline{\textbf{OverloadPT}}} $\cdot$ iOS strength-training app $|$ \emph{Swift, SwiftUI, SwiftData, Combine}}{2025}
          \resumeItemListStart
            \resumeItem{Built an iOS strength app in SwiftUI + SwiftData: a \textbf{progression engine} pre-fills next-session weights once target sets are hit, with a 102-exercise catalog across 9 muscle groups, Swift Charts trend analytics, and SwiftData persistence.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Python, SQL, Java, C, Swift} \\
     \textbf{Financial \& Domain}{: Equipment \& lease finance, amortization math (PMT/PV/FV/RATE/IRR, TValue-validated), manufacturer subsidy \& blended-rate modeling, credit-scorecard \& recovery modeling, deal-funding workflows} \\
     \textbf{Backend \& Web}{: Next.js (App Router, Server Actions), React, Node.js, FastAPI, Prisma, Tailwind, PostgreSQL (Neon), Redis, Vercel, REST APIs} \\
     \textbf{AI / Agentic}{: Agent orchestration, LLM eval pipelines, RAG + reranking, local inference (Ollama, qwen2.5), Whisper, prompt-injection mitigation} \\
     \textbf{Payments \& Integrations}{: Square (orders, payments, webhooks), Meta CAPI, Google Ads server-side conversions, Gmail / Workspace API} \\
     \textbf{Practices}{: TDD (Vitest, Playwright), CI/CD, branch-protected PRs, systemd automation, multi-tenant SaaS}
    }}
\end{itemize}

\end{document}
