%-------------------------
% Resume in Latex
% Author : Suleyman Kiani
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{1pt}
    \small +1 (289) 788-8260 $|$ \href{mailto:kianis4@mcmaster.ca}{\underline{kianis4@mcmaster.ca}} $|$
    \href{https://linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}} $|$
    \href{https://github.com/kianis4}{\underline{github.com/kianis4}} $|$
    \href{https://suleyman.io}{\underline{suleyman.io}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{Equipment-finance professional and full-stack/ML engineer who structures multi-million-dollar deals by day and ships production SaaS by night. Pursuing an MEng in Computing \& Software at McMaster. Bridges financial decision-making with intelligent systems.}
\vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Master of Engineering (MEng), Computing and Software}{Sept 2025 -- Dec 2026 (Expected)}
      \resumeItemListStart
        \resumeItem{Completed Year 1 with A+ grades in Simple Type Theory and Microservices-Oriented Architectures.}
      \resumeItemListEnd
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Applied Science (BASc), Computer Science}{Sept 2018 -- Nov 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Associate Account Manager, Equipment Finance}{Sept 2025 -- Present}
      {Mitsubishi HC Capital Canada}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Exceeded monthly funding quota every month of the current fiscal year, funding \$4M against a \$2M target (200\% of quota) in both April and May 2026.}
        \resumeItem{Structured and funded equipment deals valued at \$500K--\$3M+ using in-depth credit analysis and financial modeling, achieving a 95\% approval rate across construction and transportation sectors.}
        \resumeItem{Built financial spreads and amortization schedules in TValue, Excel, and Power BI; ran EBITDA and 4-blocker credit evaluations, improving pricing precision by 15\%.}
        \resumeItem{Streamlined origination-to-funding workflows with Salesforce Lightning automations, cutting deal turnaround by 30\%; delivered Power BI variance analysis that improved portfolio tracking accuracy by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Web Developer}{May 2021 -- Aug 2022}
      {GiftCash Inc.}{Remote}
      \resumeItemListStart
        \resumeItem{Migrated a legacy Python/Django monolith to a Node.js AWS Lambda serverless architecture, boosting scalability by 15\% and cutting infrastructure costs by 20\%.}
        \resumeItem{Optimized PostgreSQL performance via indexing, caching, and query tuning, cutting response times by 20\%; automated balance-verification workflows with Puppeteer and Axios (+25\% efficiency).}
        \resumeItem{Established Jenkins and GitHub Actions CI/CD pipelines, reducing deployment times by 30\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Applify AI} $|$ \emph{TypeScript, Next.js 15, OpenAI, Inngest, Stripe}}{Feb 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Production SaaS for AI resume tailoring serving 150+ paying users; event-driven background jobs (Inngest) run multi-minute LLM pipelines with step-level checkpointing.}
            \resumeItem{Integrated the OpenAI Responses API with Zod-validated structured outputs and achieved ~90\% inference cost reduction via prompt-cache-optimized prefixes; Stripe subscriptions and Sentry observability.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Skomp Studio} $|$ \emph{TypeScript, Next.js 15, Square, AWS, Prisma}}{Jul 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Production multi-tenant SaaS for fitness-studio management (99K+ lines of TypeScript, 500+ users, \$20K+ CAD processed) with row-level tenant isolation via a scoped Prisma client.}
            \resumeItem{Integrated Square SDK with idempotent payments and AWS SES/SNS/AppSync for email, SMS, and real-time messaging; 411 Vitest tests plus Playwright E2E on every preview.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{SKompXcel Academic Solutions} $|$ \emph{Next.js, Python, GCP}}{Jan 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Full-stack mentorship platform supporting 80+ CS students on a serverless GCP stack; 95\% grade improvement after four sessions across 1,200+ tutoring hours.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Micrograd Neural Network Framework} $|$ \emph{Python, PyTorch, Jupyter}}{Jan 2025}
          \resumeItemListStart
            \resumeItem{Built Value/Neuron/Layer/MLP components implementing automatic differentiation and backpropagation from scratch, with interactive notebooks visualizing computational graphs and gradient descent.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: TypeScript, JavaScript, Python, Swift, C, Java, SQL, PHP} \\
     \textbf{Frameworks \& Libraries}{: Next.js, React, Node.js, Tailwind CSS, Prisma, Inngest, SwiftUI, Combine, PyTorch, Django, Express} \\
     \textbf{Data \& Cloud}{: PostgreSQL, MongoDB, Redis, DynamoDB, S3; AWS (Lambda, SES, SNS, AppSync), GCP, Vercel, Docker, GitHub Actions, Jenkins, Terraform} \\
     \textbf{Finance \& Analytics}{: Credit analysis, financial modeling, EBITDA/spreads, TValue, Excel, Power BI, Salesforce}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
